Functors, CPS and monads, or how to generate efficient code from abstract designs

### 2005-04-05 paper/metamonads.tex
added a bit of related work

>>>>

Mention |Blitz++| and template meta-programming. Can do similar
eliminating of abstraction. Can even encode some domain-specific
knowledge in the form of concepts. But inlining critically depends on
the compiler's fully inlining of all methods. Furthermore, all errors
(such as type errors and concept violation errors, that is,
composition errors) are detected only when compiling the generated
code. It is immensely difficult to correlate errors (e.g., line numbers) 
to the ones in the generator itself. Furthermore, I think templates
can't be local, right? So, a lot of code generation is spread around
file-level entities.

SPIRAL does the intentional code analysis. Probably ATLAS as well.
